---
title: "Thoughts about Transit Data"
author: "Arttu Kosonen"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
bibliography:
- book.bib
- packages.bib
link-citations: yes
knit: bookdown::render_book
header-includes: \usepackage{awesomebox}
urlcolor: blue
---

# Introduction {.unnumbered}

This is a series of texts where I consider some aspects of public transport data modelling, based on my personal experience writing my Master's thesis from year 2019 on, and working at HSL (Helsinki Region Transport) as transit planner and data engineer.
In the following sections, I will discuss my thoughts about time and place representation in transit data, and what software tools I have used and like to recommend for dealing with transit data.

These texts represent my own thoughts and experiences - not exhaustive, scientifically proved facts or common best practices.
There is no answer how to best model and use transit data, and what tools to use for it - it depends!
And I've only just started my own path in the fascinating world of transit data modelling.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(knitr)
library(magrittr)
library(kableExtra)
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

## Estimated time use {.unnumbered}

For the 5 ECTS that I wish to acquire from Aalto University, I have calculated a *rough* estimate of time I've spent with topics related to these texts.
These hours come, in principle, on top of my paid working time and time spent to my Master's thesis, although they all have to do with the same topics.

```{r estimated-time-use, echo=FALSE}
tb <- read_csv('extdata/estimated-time-use.csv') %>%
  suppressMessages()

if (knitr::is_latex_output()) {
  tb %>%
    kable(format = 'latex') %>%
    column_spec(1, width = '10em') %>%
    column_spec(2, width = '25em') %>%
    column_spec(3, width = '5em')
} else {
  tb %>%
    kable()
}

```

\newpage
