---
title: "Thoughts about Transit Data"
author: "Arttu Kosonen"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"
bibliography:
- book.bib
- packages.bib
link-citations: yes
knit: bookdown::render_book
header-includes: \usepackage{awesomebox}
urlcolor: blue
---

# Introduction {.unnumbered}

This is a series of texts where I consider some aspects of public transport data modelling, based on my personal experience writing my Master's thesis from year 2019 on, and working at HSL (Helsinki Region Transport) as transit planner and data engineer.
In the following sections, I will discuss my thoughts about time and place representation in transit data, how to convert and validate real-time transit operations data for analytical use, and what software tools I have used and like to recommend for dealing with transit data.

That these texts are not exhaustive, scientifically proved facts or common best practices, but rather my own thoughts and experiences.
There is no answer how to best model and use transit data, and what tools to use for it - it depends!
And I've only just started my own path in the fascinating world of transit data modelling.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(knitr)
library(magrittr)
library(kableExtra)
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

## Estimated time use {.unnumbered}

For the 5 ECTS I wish to acquire from Aalto University with this collection of texts, I have calculated a *rough* estimate of time I've spent for different topics.
The actual work is related to my Master's thesis project for HSL and my day-to-day work at HSL thereafter.
However, during the last two years, I have spent countless hours of my own time for all these topics, to learn about them deeper than what would have been needed to just do my work at HSL.
For instance, none of the software tools I present here would be absolutely necessary for the work at HSL per se, but developing my tool skills in my free time has served both my studies and working capabilities a lot.

```{r estimated-time-use, echo=FALSE}
read_csv('extdata/estimated-time-use.csv') %>%
  suppressMessages() %>%
  kable(format = 'latex') %>%
  column_spec(1, width = '10em') %>%
  column_spec(2, width = '25em') %>%
  column_spec(3, width = '5em')
```

\newpage
